% runHistory.tex for SGR CST.

\section*{History of Runs (SGR coastwide)}

{\bf Run01}: 6 surveys (Historic GB Reed, WCHG Synoptic, HS Synoptic, QC Sound Synoptic, US Triennial, WCVI Synoptic, 0 CPUE series, $M$ and $h$ fixed. 5 selectivities estimated with uninformed priors. 2 selectivities (US Triennial,  Historic GB Reed) fixed. cvpro=c(0.4, 0.2, 0.2, 0.35, 0.35, 0.4).  Female maturity ogive: based on Females-mo(4+5+6+7)-Mat(2+) analysis. \newline  

{\bf Run02}: 6 surveys (Historic GB Reed, WCHG Synoptic, HS Synoptic, QC Sound Synoptic, US Triennial, WCVI Synoptic, 0 CPUE series, $M$ and $h$ fixed. 5 selectivities estimated with uninformed priors. 2 selectivities (US Triennial,  Historic GB Reed) fixed. cvpro=c(0.2, 0.2, 0.2, 0.2, 0.2, 0.2).  Female maturity ogive: based on Females-mo(4+5+6+7)-Mat(2+) analysis. \newline  

{\bf Run03}: 6 surveys (Historic GB Reed, WCHG Synoptic, HS Synoptic, QC Sound Synoptic, US Triennial, WCVI Synoptic, 0 CPUE series, $M$ and $h$ fixed. 5 selectivities estimated with uninformed priors. 2 selectivities (US Triennial,  Historic GB Reed) fixed. cvpro=c(0.4, 0.2, 0.2, 0.35, 0.35, 0.4).  Female maturity ogive: based on Females-mo(4+5+6+7)-Mat(3+) analysis. \newline  

{\bf Run04}: 6 surveys (Historic GB Reed, WCHG Synoptic, HS Synoptic, QC Sound Synoptic, US Triennial, WCVI Synoptic, 0 CPUE series, $M$ and $h$ fixed. 5 selectivities estimated with uninformed priors. 2 selectivities (US Triennial,  Historic GB Reed) fixed. cvpro=c(0.2, 0.2, 0.2, 0.2, 0.2, 0.2).  Female maturity ogive: based on Females-mo(4+5+6+7)-Mat(3+) analysis. \newline  

{\bf Run05}: 6 surveys in new order (WCHG Synoptic, HS Synoptic, QC Sound Synoptic, WCVI Synoptic, Historic GB Reed, US Triennial), 0 CPUE series, $M$ and $h$ fixed. 5 selectivities estimated with informed priors, based on associated POP assessment results and a 30\% CV. 2 selectivities (US Triennial,  Historic GB Reed) fixed using POP median values. cvpro=c(0.4,0.2,0.2,0.35,0.35,0.4).  Female maturity ogive: based on Females-mo(4+5+6+7)-Mat(3+) analysis. \newline  

{\bf Run06}: 6 surveys in new order (WCHG Synoptic, HS Synoptic, QC Sound Synoptic, WCVI Synoptic, Historic GB Reed, US Triennial), 0 CPUE series, $M$ and $h$ fixed. 4 survey selectivities estimated with informed priors, based on associated POP assessment results and a 30\% CV; commericial selecitivy parameters estimated with uniform prior. 2 selectivities (US Triennial,  Historic GB Reed) fixed using POP median values. cvpro=c(0.4,0.2,0.2,0.35,0.35,0.4).  Female maturity ogive: based on Females-mo(4+5+6+7)-Mat(3+) analysis. \newline  

{\bf Run07}: same as Run05, except cvpro=c(0.2, 0.2, 0.2, 0.2, 0.2, 0.2);  \newline

{\bf Run08}: same as Run06, except cvpro=c(0.2, 0.2, 0.2, 0.2, 0.2, 0.2);  \newline

{\bf Run09}: same as Run06; used cvpro=c(0.2, 0.2, 0.35, 0.4, 0.4, 0.35); fixed M=0.06, added estimated h (mean=0.674; CV=10\%); \newline

{\bf Run10}: same as Run06; used cvpro=c(0.2, 0.2, 0.35, 0.4, 0.4, 0.35); estimated M (prior mean=0.06;SD=0.006); estimated h (mean=0.674; CV=10\%); \newline

{\bf Run11}~(OLD Base Case): estimated M (prior mean=0.06;SD=0.006); estimated h (mean=0.674; CV=10\%); 6 surveys (WCHG Synoptic, HS Synoptic, QC Sound Synoptic, WCVI Synoptic, Historic GB Reed, US Triennial), 0 CPUE series; 4 synoptic survey selectivities estimated with informed priors, based on associated POP assessment results and a 30\% CV; commericial selecitivy parameters estimated with uniform prior. 2 selectivities (US Triennial,  Historic GB Reed) fixed using POP median values. cvpro=c(0.2,0.2,0.35,0.4,0.4,0.35).  Female maturity ogive: based on Females-mo(4+5+6+7)-Mat(3+) analysis; \newline 

{\bf Run12}~(OLD Sensitivity 1): same as Run11, except fix male \& female M=0.06; \newline

{\bf Run13}~(OLD Sensitivity 2): same as Run11, except except add back in the 1994 (Ocean Selector) and 1995 (Frosti + Ocean Selector index data points for the GIG Historic survey; \newline

{\bf Run14}~(OLD Sensitivity 3): same as Run11, except use steeper female maturity ogive: based on Females-mo(4+5+6+7)-Mat(2+) analysis; \newline

{\bf Run15}~(OLD Sensitivity 4): same as Run11, except estimate synoptic survey selectivities with uniform priors instead of informed priors (use same starting values as for Run 11); \newline

{\bf Run16}~(Base Case): Same as Run11 except input survey indices and CVs had to be recalculated, otherwise -- estimated M (prior mean=0.06;SD=0.006); estimated h (mean=0.674; CV=10\%); 6 surveys (WCHG Synoptic, HS Synoptic, QC Sound Synoptic, WCVI Synoptic, Historic GB Reed, US Triennial), 0 CPUE series; 4 synoptic survey selectivities estimated with informed priors, based on associated POP assessment results and a 30\% CV; commericial selecitivy parameters estimated with uniform prior. 2 selectivities (US Triennial,  Historic GB Reed) fixed using POP median values. cvpro=c(0.2,0.2,0.35,0.4,0.4,0.4).  Female maturity ogive: based on Females-mo(4+5+6+7)-Mat(3+) analysis; \newline 

{\bf Run17}~(Sensitivity 1): same as Run16, except fix male \& female M=0.06; \newline

{\bf Run18}~(Sensitivity 2): same as Run16, except except add back in the 1994 (Ocean Selector) and 1995 (Frosti + Ocean Selector index data points for the GIG Historic survey; \newline

{\bf Run19}~(Sensitivity 3): same as Run16, except use steeper female maturity ogive: based on Females-mo(4+5+6+7)-Mat(2+) analysis; \newline

{\bf Run20}~(Sensitivity 4): same as Run16, except estimate synoptic survey selectivities with uniform priors instead of informed priors (use same starting values as for Run 16); \newline

{\bf Run21}~(Sensitivity 5): same as Run16, except cvpro=c(0.2,0.2,0.2,0.2,0.2,0.2). \newline
