% Silvergray Rockfish CST base case (Run11)
\section{Bayesian MCMC Results}

The MCMC procedure performed 10,000,000 iterations, sampling every 10,000$^\mathrm{th}$ to give 1,000 MCMC samples.  The 1,000 samples were used with no burn-in period (because the MCMC searches started from the MPD values). The quantiles (0.05, 0.50, 0.95) for estimated parameters and derived quantities appear in Tables~\ref{tab:MCMCpar} and \ref{tab:MCMCderived}. In particular, the current year median estimate of $B_{\Sexpr{currYear}}$ is \Sexpr{format(median(Bcurr.MCMC),digits=0,big.mark=",",scientific=FALSE)}~t. The median depletion estimate $B_{\Sexpr{currYear}}/B_0$ is  \Sexpr{round(median(Bcurr.MCMC / B0.MCMC),3)}.

MCMC traces show acceptable convergence properties (no trend with increasing sample number) for the estimated parameters (Figure \ref{fig:traceParams}), as does a diagnostic analysis that splits the samples into three segments (Figure \ref{fig:splitChain}). Some of the parameters (e.g., $h$) move from the initial MPD estimate to some other median value.  Pairs plots of the estimated parameters (starting at Figure~\ref{fig:pairs1}) show no undesirable correlations between parameters.  In particular, steepness $h$ and the natural mortality parameter\Sexpr{if (Nsex>1) "s ($M_1$,$M_2$)" else "$M_1"} show little correlation, suggesting that sufficient data exist to estimate these parameters simultaneously.  Trace plots of the derived quantities 'female spawning biomass' (Figure~\ref{fig:traceBiomass}) and recruitment (Figure~\ref{fig:traceRecruits}) also show good convergence properties.  Thus, the MCMC computations seem satisfactory.

Marginal posterior distributions and corresponding priors for the estimated parameters are shown in Figure \ref{fig:pdfParameters}. For some of the parameters (e.g., $M_2$), the model finds enough information to move the posterior distribution away from the prior. The estimate of female natural mortality, $M_1$, shifted slightly higher from \Sexpr{round(currentRes$extra$priors$M1[1,5],3)} to \Sexpr{round(currentRes$extra$parameters$M1[1],3)} while male natural mortality, $M_2$, shifted noticeably lower from \Sexpr{round(currentRes$extra$priors$M1[2,5],3)} to \Sexpr{round(currentRes$extra$parameters$M1[2],3)}. The $h$ posterior basically mirrored the prior. Corresponding summary statistics for the estimated parameters are given in Table \ref{tab:MCMCpar}.

<<Bcalcs, results=hide, echo=FALSE>>=
BoverB0 = currentMCMC$B/currentMCMC$B[,1]
BoverB0.med = apply(BoverB0,2,median)
BoverB0.med.min = min(BoverB0.med)
BoverB0.med.min.yr = names(BoverB0.med)[grep(BoverB0.med.min,BoverB0.med)][1]

ut.med = apply(currentMCMC$U,2,median)
ut.med.max = max(ut.med,na.rm=TRUE)
ut.med.max.yr = names(ut.med)[grep(ut.med.max,ut.med)][1]
@

The marginal posterior distribution of vulnerable biomass and catch (Figure~\ref{fig:VBcatch}) shows a decline in the population from 1965 to aprroximately 1992, and a levelling off since then. 
The median spawning biomass relative to unfished equilibrium values (Figure~\ref{fig:BVBnorm}) reached a minimum of \Sexpr{round(BoverB0.med.min,3)} in \Sexpr{BoverB0.med.min.yr} and currently sits at \Sexpr{round(rev(BoverB0.med)[1],3)}. 
The recruitment patterns for Silvergray Rockfish show occasional upticks in 1982, 1991, and 2000 (Figure~\ref{fig:recruitsMCMC}). 
Exploitation rates were elevated during various periods around 1965, 1988, 1994, and peaked in \Sexpr{ut.med.max.yr} at a median value of \Sexpr{round(ut.med.max,3)} (Figure~\ref{fig:exploitMCMC}).
A phase plot showing the time-evolution of spawning biomass and exploitation rate relative to $B_\mathrm{MSY}$ and $F_\mathrm{MSY}$ (Figure~\ref{fig:snail}) show a meandering within a good zone (low exploitation, high biomass).

\section{Projection results and decision tables}

Projections were made to evaluate the future behaviour of the population under different levels of constant catch, given the model assumptions.  The projections, starting with the biomass at the beginning of \Sexpr{currYear}, were made over a range of constant catch strategies (\Sexpr{min(as.numeric(row.names(refProbs$LRP)))}-\Sexpr{prettyNum(max(as.numeric(row.names(refProbs$LRP))), big.mark=",")}~t) for each of the \numMCMC~MCMC samples in the posterior, generating future biomass trends by assuming random recruitment deviations.  Future recruitments were generated through the stock-recruitment function using recruitment deviations drawn randomly from a lognormal distribution with zero mean and constant standard deviation (see Appendix~\eqnchapter{} for full details). Projections were made for \Sexpr{dim(refProbs$LRP)[2]-1} years. This time frame was considered to be long enough to satisify the 'long-term' requirement of the Request for Science Information and Advice (Appendix~A), yet short enough for the projected recruitments to be mainly based on individuals spawned before \Sexpr{currYear} (and hence already estimated by the model).

Resulting projections of spawning biomass are shown for selected catch strategies (Figure \ref{fig:Bproj}). These suggest that the recent increase in spawning biomass would most likely continue for a catch of \Sexpr{onePolicy}~t, which is \Sexpr{paste(ifelse(onePolicy>recentCatchMean," larger "," smaller "))} than the recent average catch of \Sexpr{round(recentCatchMean)}~t. 

Note that recruitment is drawn from the estimated stock-recruitment curve with lognormal error that has a standard deviation of \Sexpr{sigmaR} and a mean of zero. However, this approach of average recruitment does not accurately simulate the occasional large recruitment events that have occurred for this stock (Figure~\ref{fig:recruitsMCMC}).

Decision tables give the probabilities of the spawning biomass exceeding the reference points in specified years, calculated by counting the proportion of MCMC samples for which the biomass exceeded the given reference point.

Results for the three $\Bmsy$-based reference points are presented in Tables \ref{tab:LRP}-\ref{tab:Bmsy}. For example, the estimated probability that the stock is in the provisional healthy zone in 2017 under a constant catch strategy of 1,000~t is P$(B_{2017} > 0.8 \Bmsy)=\Sexpr{round(refProbs$URP["1000","2017"], dig=2)}$ (row '1000' and column '2017' in Table \ref{tab:URP}). 

Table~\ref{tab:Bcurr} provides probabilities that projected spawning biomass $B_t$ will exceed the current-year biomass $B_{\Sexpr{currYear}}$ at the various catch levels. The first column populated by zero values simply means that the current-year biomass will never be greater than itself. Table~\ref{tab:umsy} shows the probabilities of projected exploitation rate $u_t$ exceeding that at MSY ($u_\mathrm{MSY}$).

For the maximum sustainable yield (MSY) calculations, projections were run for \Sexpr{currentMSY$maxUind[1]} values of constant exploitation rate $u_t$ between \Sexpr{currentMSY$uMin[1]} and \Sexpr{currentMSY$uMax[1]}, until an equilibrium yield was reached within a tolerance of \Sexpr{currentMSY$tolerance[1]}~t (or until \Sexpr{prettyNum(currentMSY$maxProj[1], big.mark=",")} years had been reached). This was done for each of the \numMCMC~samples.
The lower bound of $u_t$ was reached for \Sexpr{ifelse(sum(currentMSY$imsy==1)==0," none ",sum(currentMSY$imsy==1))} of the MCMC samples, and the upper bound was reached by \Sexpr{ifelse(sum(currentMSY$imsy==currentMSY$maxUind[1])==0," none ",sum(currentMSY$imsy==currentMSY$maxUind[1]))} of the samples.
Of the \Sexpr{prettyNum(currentMSY$maxUind[1] * num.MCMC, big.mark=",")} projection calculations, \Sexpr{ifelse(sum(currentMSY$nProjMatTF)==0," all converged ",paste(sum(currentMSY$nProjMatTF)," did not converge ",sep=""))} by \Sexpr{prettyNum(currentMSY$maxProj[1], big.mark=",")} years.

% End of Appendix G

