% runHistory.tex for SGR CST.

\section*{History of Runs (SGR coastwide}

{\bf Run01}: 6 surveys (Historic GB Reed, WCHG Synoptic, HS Synoptic, QC Sound Synoptic, US Triennial, WCVI Synoptic, 0 CPUE series, $M$ and $h$ fixed. 5 selectivities estimated with uninformed priors. 2 selectivities (US Triennial,  Historic GB Reed) fixed. cvpro=c(0.4, 0.2, 0.2, 0.35, 0.35, 0.4).  Female maturity ogive: based on Females-mo(4+5+6+7)-Mat(2+) analysis. \newline  

{\bf Run02}: 6 surveys (Historic GB Reed, WCHG Synoptic, HS Synoptic, QC Sound Synoptic, US Triennial, WCVI Synoptic, 0 CPUE series, $M$ and $h$ fixed. 5 selectivities estimated with uninformed priors. 2 selectivities (US Triennial,  Historic GB Reed) fixed. cvpro=c(0.2, 0.2, 0.2, 0.2, 0.2, 0.2).  Female maturity ogive: based on Females-mo(4+5+6+7)-Mat(2+) analysis. \newline  

{\bf Run03}: 6 surveys (Historic GB Reed, WCHG Synoptic, HS Synoptic, QC Sound Synoptic, US Triennial, WCVI Synoptic, 0 CPUE series, $M$ and $h$ fixed. 5 selectivities estimated with uninformed priors. 2 selectivities (US Triennial,  Historic GB Reed) fixed. cvpro=c(0.4, 0.2, 0.2, 0.35, 0.35, 0.4).  Female maturity ogive: based on Females-mo(4+5+6+7)-Mat(3+) analysis. \newline  

{\bf Run04}: 6 surveys (Historic GB Reed, WCHG Synoptic, HS Synoptic, QC Sound Synoptic, US Triennial, WCVI Synoptic, 0 CPUE series, $M$ and $h$ fixed. 5 selectivities estimated with uninformed priors. 2 selectivities (US Triennial,  Historic GB Reed) fixed. cvpro=c(0.2, 0.2, 0.2, 0.2, 0.2, 0.2).  Female maturity ogive: based on Females-mo(4+5+6+7)-Mat(3+) analysis. \newline  

{\bf Run05}: 6 surveys (Historic GB Reed, WCHG Synoptic, HS Synoptic, QC Sound Synoptic, US Triennial, WCVI Synoptic, 0 CPUE series, $M$ and $h$ fixed. 5 selectivities estimated with informed priors, based on associated POP assessment results and a 30\% CV. 2 selectivities (US Triennial,  Historic GB Reed) fixed using POP median values. cvpro=c(0.4,0.2,0.2,0.35,0.35,0.4).  Female maturity ogive: based on Females-mo(4+5+6+7)-Mat(3+) analysis. \newline  




